---
title: "Reproducible Pitch Presentation"
author: "Manoj Pradhan"
date: "July 17, 2017"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Introduction

This presentation is part of the Course Project for the Coursera Developing Data Products class. The peer assessed assignment has two parts. 
- we need to create a Shiny application and deploy it on Rstudio's servers. 
- we should use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about the application. 

####How to Access

The app developed for the first part of the assignment is avalilable at:
https://pradhanmk1.shinyapps.io/diamondApp/

Source code for ui.R and server.R files are available on the GitHub:
https://github.com/pradhanmk1/dataproducts

#### About the Data

This app use dataset containing the prices and other attributes of almost 54,000 diamonds
```{r data, include=TRUE}
library(ggplot2)
head(diamonds)
```

####About the App

Diamond Explorer based on different available parameters

####Input of the App

User will supply sample size of data, x axis values, y axis values, color of diamondto get the graph on the selected parameter.

User can also check on/off on the ?Jitter/Smooth? box to show the  view on the graph.
user can  provide facet row/facet column values as well to get the graph accordingly.



## The ui.R 

* It uses the fluidPage layout.
* Slider input for sample size of diamonds data
<br />
  sliderInput('sampleSize', 'Sample Size', min=1, max=nrow(dataset),value=min(1000, nrow(dataset)), step=500, round=0)
* Select input for X axis,y axis,color,facet_row and facet_column
<br />
  selectInput('x', 'X', names(dataset))
<br />
  selectInput('y', 'Y', names(dataset), names(dataset)[[2]])<br />
  selectInput('color', 'Color', c('None', names(dataset)))<br />
  selectInput('facet_row', 'Facet Row', c(None='.', names(dataset)))<br />
  selectInput('facet_col', 'Facet Column', c(None='.', names(dataset)))<br />
* checkbox input for jitter or smooth option of plot
<br />
  checkboxInput('jitter', 'Jitter')<br />
  checkboxInput('smooth', 'Smooth')


## The server.R

The app will present the result in a scatter plot.

* uses ggplot for ploting<br />
  ggplot(dataset(), aes_string(x=input$x, y=input$y)) + geom_point()
* uses color,facet_grid,geom_jitter or geom_smooth based on the interactive input<br />
- color <br />
  aes_string(color=input$color)<br />
- facet row and facet column<br />
  facets <- paste(input$ facet_row, '~', input$ facet_col)<br />
  facet_grid(facets)
- jitter<br />
  geom_jitter()<br />
- smooth<br />
  geom_smooth()

## Deployment

1.  Created Account in Shinyapps.io
2.  Run the setAccountInfo
3.  library(rsconnect)
4.  library(shiny)
5.  deployApp("/Shiny_App") or runAPP the shiny R application and publish to Rpub

It generated the Application file https://pradhanmk1.shinyapps.io/diamondApp/